Lasso_RCI_Response

### 2024-01-30 Lasso_RCI_Response.Rmd
Updated Tables

## Part 1: Who is attending?
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of prepost change???
- Table 4: demographic breakdown
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         !is.na(RESPONDER_FIGS)
        )

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
Demo_tab

# Treatment info
resp_tab <- data.frame(table1::table1(
  ~Referral_1 + DC_status_1 + RIPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab

# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
                                     data = Mothership_post))
Dis_tab

#Full demographic break down.
CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
CODis_tab

Mothership_post$Current_Dx
```

>>>>

## Part 1: Who is attending?

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of prepost change???
- Table 4: demographic breakdown
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         !is.na(RESPONDER_FIGS)
        )

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
Demo_tab
```

### Treatment information
```{r}
# PHP Treatment information
resp_tab <- data.frame(table1::table1(
  ~Referral_1 + DC_status_1 + RIPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab

# Treatment scores 
Scores_tab <- data.frame(matrix(nrow = 8,ncol=4))
colnames(Scores_tab) = c("Variables", "Pre M(SD)", "Post M(SD)", "Change M(SD)")

    #CUXOS
      Scores_tab[1,] = 
        c("CUXOS",
          paste0(round(mean(Mothership_post$CUXOS_pre),2), " (", round(sd(Mothership_post$CUXOS_pre),2),")"),
          paste0(round(mean(Mothership_post$CUXOS_post),2), " (", round(sd(Mothership_post$CUXOS_post),2),")"),
          paste0(round(mean(Mothership_post$Delta_Anx_DC),2), "(",round(sd(Mothership_post$Delta_Anx_DC),2),")")
        )

    #CUDOS
      Scores_tab[2,] = 
        c("CUDOS",
          paste0(round(mean(Mothership_post$CUDOS_pre),2), " (", round(sd(Mothership_post$CUDOS_pre),2),")"),
          paste0(round(mean(Mothership_post$CUDOS_post),2), " (", round(sd(Mothership_post$CUDOS_post),2),")"),
          paste0(round(mean(Mothership_post$Delta_Dep_DC),2), "(",round(sd(Mothership_post$Delta_Dep_DC),2),")")
        )

    #RDQ total
      # Scores_tab[3,] = 
      #    c("RDQ Total",
      #     paste0(round(mean(Mothership_post$RDQ_Pre_Total),2), " (", round(sd(Mothership_post$RDQ_Pre_Total),2),")"),
      #     paste0(round(mean(Mothership_post$RDQ_Post_Total),2), " (", round(sd(Mothership_post$RDQ_Post_Total),2),")"),
      #     paste0(round(mean(Mothership_post$RDQ_Change_Total),2), "(",round(sd(Mothership_post$RDQ_Change_Total),2),")")
      #    )

    #RDQ Subscales
      Scores_tab[3,] = c ("RDQ Subscales", NA, NA, NA)

    #Coping
      Scores_tab[4,] = 
        c("Coping ability",
          paste0(round(mean(Mothership_post$rdqPRE_coping, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_coping, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdqPOST_coping, na.rm = TRUE),2), " (",round(sd(Mothership_post$rdqPOST_coping, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdq_coping_change, na.rm = TRUE),2),"(",round(sd(Mothership_post$rdq_coping_change, na.rm = TRUE),2),")")
        )

    #"PMH"
        Scores_tab[5,] = 
        c("Positive mental health",
          paste0(round(mean(Mothership_post$rdqPRE_coping, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_coping, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdqPOST_coping, na.rm = TRUE),2), " (",round(sd(Mothership_post$rdqPOST_coping, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdq_coping_change, na.rm = TRUE),2),"(",round(sd(Mothership_post$rdq_coping_change, na.rm = TRUE),2),")")
        )

    # functioning
            Scores_tab[6,] = 
        c("Functioning",
          paste0(round(mean(Mothership_post$rdqPRE_func, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_func, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdqPOST_func, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPOST_func, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdq_func_change, na.rm = TRUE),2), "(",round(sd(Mothership_post$rdq_func_change, na.rm = TRUE),2),")")
        )

    # General sense of wellbeing
            Scores_tab[7,] = 
        c("General sense of wellbeing",
          paste0(round(mean(Mothership_post$rdqPRE_wbs, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_wbs, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdqPOST_wbs, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPOST_wbs, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdq_wbs_change, na.rm = TRUE),2), "(",round(sd(Mothership_post$rdq_wbs_change, na.rm = TRUE),2),")")
        )

    #Symptoms"
            Scores_tab[8,] = 
        c("Symptoms",
          paste0(round(mean(Mothership_post$rdqPRE_sym, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_sym, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdqPOST_sym, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPOST_sym, na.rm = TRUE),2),")"),
          paste0(round(mean(Mothership_post$rdq_sym_change, na.rm = TRUE),2), "(",round(sd(Mothership_post$rdq_sym_change, na.rm = TRUE),2),")")
        )

 Scores_tab
```

### Disorder Breakdowns
Here are some tables displaying info on the psychiatric disorders treated at the PHP
```{r}
# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
                                     data = Mothership_post))
colnames(Dis_tab) = c("Variables","Non Responder", "Responder", "Total")
Dis_tab

#Full demographic break down
co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat))

CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
colnames(CODis_tab)[1] = c("Variables")
CODis_tab
```
